Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment

### 2024-08-02 JASA-template.tex
Update (Matthias).

\subsection{Robust Bayesian Analysis}

@@

\added{%
For instance, assume $\underline{k}$ and $\overline{k}$ represent the expert's bounds of the prior expectation on the
total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
}

\added{%
We may also use the empirically observed correlations from the data directly.
This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
When doing so, we need
% \added{
a prior judgement on what is a reasonable
%}
correlation between active predictors and the outcome.
Say the expert judges that
an active predictor has a correlation with the outcome
that is typically between $\underline{c}$ and $\overline{c}$.
Let $\overline{k}$ be the number of predictors with marginal correlation greater than $\underline{c}$
and $\underline{k}$ be number of predictors with marginal 
correlation greater than $\overline{c}$.
%%% MT to TB: in retrospect, using \underline{k} to lower bound the
%%% number of active variables is a bit strange... it seems like we're
%%% treating variables with "too high" correlations as inactive;
%%% should we simply set \underline{k} directly (e.g. 0, 1, or higher
%%% if suitable) instead of using the correlations?
As before, we can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
}

@@

\added{%
To elicit $\mathcal{P}$,
as discussed earlier,
we use the empirically observed correlations from the data directly.
We assume that, through expert elicitation,
an active predictor has a correlation with the outcome
that is typically between $0.15$ and $0.35$.
Let $\overline{k}$ be the number of predictors with marginal correlation greater than $0.15$
and let $\underline{k}$ be number of predictors with marginal 
correlation greater than $0.35$.
Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%
}

>>>>

\subsection{Robust Bayesian Analysis}
\label{sec:robustbayesanalysis}

@@

\added{%
For instance, assume $\underline{k}$ and $\overline{k}$ represent the expert's bounds of the prior expectation on the
total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.
Using an interval for the prior expectation on the total number of active variables
gives us a more cautious approach to specifying the prior distribution on variable selection,
and thus more robust inferences.%
}

%%% TODO MT: add in review.txt
\added{%
Alternatively, we may also use the empirically observed correlations from the data directly.
This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
When doing so, we need
% \added{
a prior judgement on what is a reasonable
%}
correlation between active predictors and the outcome.
Say the expert judges that
an active predictor has a correlation with the outcome
that lies typically in $[-1,-c]\cup[c,1]$, i.e.
an absolute correlation larger than $c$.
Let $k_c$ be the number of predictors with absolute marginal correlation greater than $c$.
We could then consider $q=k_c/p$ for the prior, as it gives a prior estimate on the selection probability that is consistent with a prior predictive expectation of $k_c$ active variables.
Now, it is in general quite difficult to specify an exact value for $c$ a priori.
Therefore, we consider an interval $[\underline{c},\overline{c}]$ for $c$, leading to
$q\in \left[k_{\overline{c}}/p, k_{\underline{c}}/p\right]$
(note that $k_c$ is monotonically non-increasing in $c$).
}

@@

\added{%
To elicit $\mathcal{P}$,
as discussed earlier in \cref{sec:robustbayesanalysis},
we use the empirically observed correlations from the data directly.
We assume that, through expert elicitation,
an active predictor has an absolute correlation with the outcome
that is typically larger than a value lying in the interval $[0.15,0.35]$
*** TODO TB cite some papers with values consistent with this ***.
Let $\overline{k}$ be the number of predictors with absolute marginal correlation greater than $0.15$
and let $\underline{k}$ be number of predictors with absolute marginal correlation greater than $0.35$.
Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%
}
